Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives

### 2015-01-27 paper/Diversity_MS.tex
Edited manuscript

@@

	Although tenrecs are often cited as an example of both an adaptive radiation and exceptional convergent evolution, these claims have not been investigated quantitatively. There are qualitative similarities among the hind limb morphologies of tenrecs and several other unrelated species with similar locomotory styles \citep{Salton2009} but the degree of morphological similarity has not been established. Morphological diversity is an important feature of adaptive radiations \citep{Losos2010a} and it also informs our understanding of convergent phenotypes \citep{Muschick2012}. Therefore, it is important to quantify patterns of morphological diversity in tenrecs to gain an insight into their evolution. My thesis is the first study to address this issue.

	We present the first quantitative study of patterns of morphological diversity in tenrecs. We use geometric morphometric techniques \citep{Rohlf1993} to compare cranial morphological diversity in tenrecs to that of their closest relatives, the golden moles (Afrosoricida, Chrysochloridae). 
	We expect tenrecs to be more morphologically diverse than golden moles because tenrecs occupy a wider variety of ecological niches. The tenrec Family includes terrestrial, semi-fossorial, semi-aquatic and semi-arboreal species \citep{Soarimalala2011}. In contrast, all golden moles occupy very similar, fossorial ecological niches \citep{Bronner1995}. Greater ecological variety is often (though not always) correlated with higher morphological diversity \citep{Losos2010a}.

	%Finish off this introduction
%************************************
\section{Materials and Methods}

%Overview section: data, geometric morphometrics, measuring diversity

	The methods we used involved several steps of data collection, geometric morphometrics analyses and comparisons of morphological diversity. These included i) data collection, ii)geometric morphometric analyses and iii)estimating morphological diversity. For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.

@@

	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}. 
	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures along with the mandibles \citep{Finlay2013m}. Copyright restrictions from the other museums prevent public sharing of their images however they are available on request.

@@

	We used a combination of landmark and semilandmark analysis approaches to assess the shape variability in skull.  We used the TPS software suite \citep{Rohlf2013} to digitise landmarks and curves on the photos. We set the scale on each image individually to standardise for the different camera heights that I used when photographing my specimens. We created separate data files for each of the three morphometric analyses (skulls in dorsal, ventral and lateral views). One of us (SF) digitised landmarks and semilandmark points on every image individually. Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis. We photographed 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).

	When using semilandmark approaches there is a potential problem of over - sampling: simpler structures will require fewer semilandmarks to accurately represent their shape  \citep{MacLeod2012}. To ensure that we applied a uniform standard of shape representation to each outline segment (i.e. that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}. For each data set we chose a random selection of photos of specimens which represented the breadth of the morphological data (i.e. specimens from each sub-group of species). We drew the appropriate curves on each specimen and over-sampled the number of points on the curves. We measured the length of the line and regarded that as the 100\%, true length of that outline. We then re-sampled the curves with decreasing numbers of points and measured the length of the outlines. We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file. We continued this process until I found the minimum number of points that gave a curve length which was at least 95\% accurate.  We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.

@@

	%Maybe put morphometrics error checking into the supplementary as well?
	%Put the landmark tables into supplementary
%***************************************************

	After creating the files with the landmarks and semilandmarks placed on each photograph, we used TPSUtil \citep{Rohlf2012} to create "sliders" files that defined which points in the TPS files should be treated as semilandmarks \citep{Zelditch2012}. We combined the landmarks and taxonomic identification files into a single morphometrics data object and carried out all further analyses in R version 3.1.1 \citep{Team2014}. Data and code for all of our analyses is available on GitHub (REF to paper repository).

	At this stage, we either used the full data set (31 species of tenrec and 12 species of golden mole) or a reduced data set with just 17 species of tenrec (Figure \ref{fig:flow}). We created this reduced data set because the majority of tenrec species (19 out of 31 in my data) belong to the \textit{Microgale} (shrew-like) Genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}. This may mask signals of higher morphological diversity among other tenrecs. To test this, we created a subset of the tenrec data that included just five of the \textit{Microgale} species, each representing one of the five sub-divisions of \textit{Microgale} outlined by Soarimalala and Goodman \citeyearpar{Soarimalala2011}, i.e. small, small-medium, medium, large and long-tailed species. We compared the morphological diversity of this subset of tenrecs (n=17: five \textit{Microgale} and 12 non-\textit{Microgale} species) to that of the 12 species of golden moles (dashed arrows in Figure \ref{fig:flow}). After this selection stage, all further steps in the analyses were the same.

@@

	We tested the null hypothesis that tenrecs and golden moles have the same morphological diversity (the same mean Euclidean distance to the Family centroid). If this is true, when we randomly assign the group identity of each species (i.e. shuffle the "tenrec" and "golden mole" labels) and then re-compare the morphological diversity of the two groups, there will be no significant difference between these results and those obtained when the species are assigned to the correct groupings. 
	We performed this shuffling procedure (random assignation of group identity) 1000 times and calculated the difference in morphological diversity between the two groups for each permutation. This generated a distribution of 1000 values which are calculations of the differences in morphological diversity under the assumption that the null hypothesis (equal morphological diversity in the two Families) is true. This method automatically accounts for differences in sample size because shuffling of the group labels preserves the sample size of each group: there will always be 12 species labelled as "golden mole" and then, depending on the analysis, either 31 or 17 species labelled as "tenrec". Therefore, the 1000 permuted values of differences in morphological diversity create a distribution of the expected difference in diversity between a group of sample size 31 (or 17 in the case of the subsetted tenrec data) compared to a group of sample size 12 under the null hypothesis that the two groups have the same morphological diversity. We compared the observed measures of the differences in morphological diversity between the two Families to these null distributions to determine whether there were significant differences after taking sample size into account (two-tailed t test).
%*********************************
\section{Results and Discussion} %PeerJ asks for these two sections to go together

\subsection{Results}
	Figure \ref{fig:threePCA} depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies. The PCAs are based on the average Procrustes -superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
%-----------------------------
%PCA figure with three plots
%PCA figure
	%From the diversity_PCAplots_3panel
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/PCA_threeplot.png}
	\caption[Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls.]
		{Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for the skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views. Each point represents the average skull shape of an individual species. Axes are principal component 1 (PC1) and principal component 2 (PC2) of the average scores from principal components analyses of mean Procrustes shape coordinates for each species.}
	\label{fig:threePCA}
	\end{figure}
%--------------------------
	To compare morphological diversity in the two families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes). First, we compared the position of each Family within the morphospace plots. Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{fig:threePCA}.

@@

%---------------------------------------------
	The pairwise permutation tests for each analysis confirmed that differences in morphological diversity were not artefacts of differences in sample size (Table \ref{tab:permutations})
%--------------------------------------------	
\begin{table}[!htbp]			
	\caption[Results of the permutation tests]{Results of the permutation analyses comparing the observed differences in morphological diversity to a null distribution of expected results. Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid. Results are shown for both the full (N=31 species of tenrec compared to 12 species of golden mole) and reduced (N=17 species of tenrec compared to 12 golden moles) data sets. Significant values (p$<$0.05) indicate that the observed morphological diversity is different to the expected differences under a null hypothesis of equivalent diversities in the two Families.}
		\input{tables/perm.results} 
		\label{tab:permutations}  
	\end{table}
%----------------------------------
\subsection{Discussion}
%Could change this to conclusions
	Tenrecs are often cited as an example of a mammalian group with high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}. They are also more ecologically diverse than their closest relatives \citep{Soarimalala2011, Bronner1995} so we predicted that they would be more morphologically diverse than golden moles. However, our results do not support our original prediction, highlighting the importance of quantitative tests of perceived morphological patterns.

	In our full analysis, tenrecs only had higher morphological diversity than golden moles when the skulls were measured in lateral view (Table \ref{tab:diversity}). There was no difference in morphological diversity when we analysed the skulls in dorsal or ventral views. This is most likely due to our choice of landmarks. The two outline curves in lateral view (Figure REF) emphasise morphological variation in the back and top of the skulls. These curves summarise overall shape variation but they do not identify clear anatomical differences because they are defined by relative features rather than homologous structures \citep{Zelditch2012}. Therefore, high morphological diversity in tenrecs when analysed in this view may not indicate biologically or ecologically relevant variation.	
	These lateral aspects of the skull morphology were not visible in the dorsal and ventral photographs so they could not be included in those analyses. In contrast, our landmarks in the dorsal, and particularly ventral, views focus on morphological variation in the overall outline shape of the sides of the skull and palate (Figure REF). The result that tenrecs are no more diverse than golden moles in these areas makes intuitive sense: most tenrecs have broad, non-specialised diets \citep{Olson2013} so there is no obvious functional reason why they should have particularly diverse palate morphologies.
	The different results for our analysis of lateral skull morphologies compared to dorsal and ventral views highlight the importance of using multiple approaches when studying 3D morphological shape using 2D geometric morphometrics techniques \citep{Arnqvist1998}.

	In addition to the differences among the three skull views, our results indicate that, in skulls at least, the overall morphological diversity within tenrecs is not as large as is often assumed \citep[e.g.][]{Eisenberg1969, Olson2013}. Studies of morphological variation are sensitive to the sampling used. If a particular morphotype is over-represented then the similarities among those species will reduce the overall morphological variation within the group \citep{Foote1991}. This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table \ref{tab:diversity}).
	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears. Of course our results are based on skull shape only and analyses of other morphological traits may produce different results, but they do provide an insight into the differences between subjective and quantitative assessments of morphological diversity.

	\subsection{Caveats} %May need to reduce this one down, and probably take it out of its own separate section

	As highlighted above, landmark choice and placement will inevitably influence the results of a geometric morphometrics study. Our interest in broad-scale, cross-taxonomic comparisons of cranial morphology constrained our choice of landmarks to those that could be accurately identified in many different species \citep[e.g.][]{Ruta2013, Goswami2011, Wroe2007}. In contrast, studies that use skulls to characterise morphological variation within species \citep[e.g.][]{Blagojevic2011, Bornholdt2008} or to delineate species boundaries within a clade \citep[e.g.][]{Panchetti2008} tend to focus on more detailed, biologically homologous landmarks \citep{Zelditch2012}. Repeating our analyses with a narrower taxonomic focus may give greater insight into the specific morphological differences among subgroups of tenrecs and golden moles.

	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}. However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}. Variation in skull shape is only one aspect of overall morphology. Quantifying variation in other morphological traits could yield different patterns. Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
%**********************************
\section{Conclusions}
	We have presented the first quantitative investigation of morphological diversity in tenrecs. Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the Family. Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required. However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs. 
%*******************************
\section{Acknowledgements} %PeerJ have a separate section for funding acknowledgements
	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments. Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
%********************************
\bibliographystyle{sysbio} 
\bibliography{refs_paper}

>>>>

%This is the abstract from my thesis

	%Patterns of morphological diversity (the variety of physical form) have important implications for our understanding of species ecology and evolution. Some clades such as cichlid fish and anole lizards are known for their high morphological diversity. Studying these groups can provide insights into the processes that led to the evolution of this exceptional diversity. 
	%Morphological diversity is often studied qualitatively. However, to truly understand the evolution of diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments. Here, we present a quantitative analysis of morphological diversity in a Family of small mammals, the tenrecs (Afrosoricida, Tenrecidae). 
	%Tenrecs are often cited as an example of an exceptionally morphologically diverse group. However, this assumption has not been tested quantitatively. We use geometric morphometric analyses of skull shape to test whether tenrecs are more morphologically diverse than their closest relatives, the golden moles (Afrosoricida, Chrysochloridae). Tenrecs occupy a wider range of ecological niches than golden moles so we predicted that they would be more morphologically diverse. 
	%Contrary to our expectations, We found that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view. Furthermore, similarities among the species-rich \textit{Microgale} tenrec Genus appear to mask higher morphological diversity in the rest of the Family. These results reveal new insights into the morphological diversity of tenrecs and highlight the importance of using quantitative methods to test qualitative assumptions about patterns of morphological diversity.

@@

	Although tenrecs are often cited as an example of both an adaptive radiation and exceptional convergent evolution, these claims have not been investigated quantitatively. There are qualitative similarities among the hind limb morphologies of tenrecs and several other unrelated species with similar locomotory styles \citep{Salton2009} but the degree of morphological similarity has not been established. Morphological diversity is an important feature of adaptive radiations \citep{Losos2010a} and it also informs our understanding of convergent phenotypes \citep{Muschick2012}. Therefore, it is important to quantify patterns of morphological diversity in tenrecs to gain an insight into their evolution.

	We present the first quantitative study of patterns of morphological diversity in tenrecs. We use geometric morphometric techniques \citep{Rohlf1993} to compare cranial morphological diversity in tenrecs to that of their closest relatives, the golden moles (Afrosoricida, Chrysochloridae). 
	We expect tenrecs to be more morphologically diverse than golden moles because tenrecs occupy a wider variety of ecological niches. The tenrec Family includes terrestrial, semi-fossorial, semi-aquatic and semi-arboreal species \citep{Soarimalala2011}. In contrast, all golden moles occupy very similar, fossorial ecological niches \citep{Bronner1995}. Greater ecological variety is often (though not always) correlated with higher morphological diversity \citep{Losos2010a}. 
	However, our results reveal that, in skulls at least, morphological diversity in tenrecs is not as great as it first appears.

	%Might need more to finish off the introduction?
%************************************
\section{Materials and Methods}

	The methods we used involved several steps of i) data collection, ii) geometric morphometric analyses and iii) estimating morphological diversity. For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.

@@

	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}. 
	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures. Copyright restrictions from the other museums prevent public sharing of their images but they are available on request.

@@

	We used a combination of landmark and semilandmark analysis approaches to assess the shape variability in the skulls.  We used the TPS software suite \citep{Rohlf2013} to digitise landmarks and curves on the photos. We set the scale on each image individually to standardise for the different camera heights used when photographing the specimens. We created separate data files for each of the three morphometric analyses (skulls in dorsal, ventral and lateral views). One of us (SF) digitised landmarks and semilandmark points on every image individually. Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis. Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).

%Maybe move this to the supplementary?
	When using semilandmark approaches there is a potential problem of over - sampling: simpler structures will require fewer semilandmarks to accurately represent their shape  \citep{MacLeod2012}. To ensure that we applied a uniform standard of shape representation to each outline segment (i.e. that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}. For each data set we chose a random selection of photos of specimens which represented the breadth of the morphological data (i.e. specimens from each sub-group of species). We drew the appropriate curves on each specimen and over-sampled the number of points on the curves. We measured the length of the line and regarded that as the 100\%, true length of that outline. We then re-sampled the curves with decreasing numbers of points and measured the length of the outlines. We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file. We continued this process until we found the minimum number of points that gave a curve length which was at least 95\% accurate.  We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.

@@

%***************************************************

	After creating the files with the landmarks and semilandmarks placed on each photograph, we used TPSUtil \citep{Rohlf2012} to create "sliders" files that defined which points in the TPS files should be treated as semilandmarks \citep{Zelditch2012}. We combined the landmarks and taxonomic identification files into a single morphometrics data object and carried out all further analyses in R version 3.1.1 \citep{Team2014}. Data and code for all of our analyses is available on GitHub \citep{Finlay2015c}.

	At this stage, we either used the full data set (31 species of tenrec and 12 species of golden mole) or a reduced data set with just 17 species of tenrec (Figure \ref{fig:flow}). We created this reduced data set because the majority of tenrec species (19 out of 31 in our data) belong to the \textit{Microgale} (shrew-like) Genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}. This may mask signals of higher morphological diversity among other tenrecs. To test this, we created a subset of the tenrec data that included just five of the \textit{Microgale} species, each representing one of the five sub-divisions of \textit{Microgale} outlined by Soarimalala and Goodman \citeyearpar{Soarimalala2011}, i.e. small, small-medium, medium, large and long-tailed species. We compared the morphological diversity of this subset of tenrecs (n=17: five \textit{Microgale} and 12 non-\textit{Microgale} species) to that of the 12 species of golden moles (dashed arrows in Figure \ref{fig:flow}). After this selection stage, all further steps in the analyses were the same.

@@

	We tested the null hypothesis that tenrecs and golden moles have the same morphological diversity (the same mean Euclidean distance to the Family centroid). If this is true, when we randomly assign the group identity of each species (i.e. shuffle the "tenrec" and "golden mole" labels) and then re-compare the morphological diversity of the two groups, there would be no significant difference between these results and those obtained when the species are assigned to the correct groupings. 
	We performed this shuffling procedure (random assignation of group identity) 1000 times and calculated the difference in morphological diversity between the two groups for each permutation. This generated a distribution of 1000 values which are calculations of the differences in morphological diversity under the assumption that the null hypothesis (equal morphological diversity in the two Families) is true. This method automatically accounts for differences in sample size because shuffling of the group labels preserves the sample size of each group: there will always be 12 species labelled as "golden mole" and then, depending on the analysis, either 31 or 17 species labelled as "tenrec". Therefore, the 1000 permuted values of differences in morphological diversity create a distribution of the expected difference in diversity between a group of sample size 31 (or 17 in the case of the subsetted tenrec data) compared to a group of sample size 12 under the null hypothesis that the two groups have the same morphological diversity. We compared the observed measures of the differences in morphological diversity between the two Families to these null distributions to determine whether there were significant differences after taking sample size into account (two-tailed t test).
%*********************************
\section{Results} %PeerJ lists results and discussion together but I think it makes more sense to keep them separate
	Figure \ref{fig:threePCA} depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies. The PCAs are based on the average Procrustes -superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
%-----------------------------
%PCA figure with three plots
%PCA figure
	%From the diversity_PCAplots_3panel
	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/PCA_threeplot.png}
	\caption[Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls.]
		{Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for the skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views. Each point represents the average skull shape of an individual species. Axes are principal component 1 (PC1) and principal component 2 (PC2) of the average scores from principal components analyses of mean Procrustes shape coordinates for each species.}
	\label{fig:threePCA}
	\end{figure}
%--------------------------
	To compare morphological diversity in the two Families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes). First, we compared the position of each Family within the morphospace plots. Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{fig:threePCA}.

@@

%---------------------------------------------
	The pairwise permutation tests for each analysis confirmed that differences in morphological diversity were not artefacts of differences in sample size (Table \ref{tab:permutations})
%--------------------------------------------	
\begin{table}[!htbp]			
	\caption[Results of the permutation tests]{Results of the permutation analyses comparing the observed differences in morphological diversity to a null distribution of expected results. Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid. Results are shown for both the full (N=31 species of tenrec compared to 12 species of golden mole) and reduced (N=17 species of tenrec compared to 12 golden moles) data sets. Significant values (p$<$0.05) indicate that the observed morphological diversity is different to the expected differences under a null hypothesis of equivalent diversities in the two Families.}
		\input{tables/perm.results} 
		\label{tab:permutations}  
	\end{table}
%----------------------------------
\section{Discussion}
%Could move this paragraph to the conclusions
	Tenrecs are often cited as an example of a mammalian group with high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}. They are also more ecologically diverse than their closest relatives \citep{Soarimalala2011, Bronner1995} so we predicted that they would be more morphologically diverse than golden moles. However, our results do not support our original prediction, highlighting the importance of quantitative tests of perceived morphological patterns.

	In our full analysis, tenrecs only had higher morphological diversity than golden moles when the skulls were measured in lateral view (Table \ref{tab:diversity}). There was no difference in morphological diversity when we analysed the skulls in dorsal or ventral views. This is most likely due to our choice of landmarks. The two outline curves in lateral view (Figure \ref{fig:landmarks}) emphasise morphological variation in the back and top of the skulls. These curves summarise overall shape variation but they do not identify clear anatomical differences because they are defined by relative features rather than homologous structures \citep{Zelditch2012}. Therefore, high morphological diversity in tenrecs when analysed in this view may not indicate biologically or ecologically relevant variation.	
	These lateral aspects of the skull morphology were not visible in the dorsal and ventral photographs so they could not be included in those analyses. In contrast, our landmarks in the dorsal, and particularly ventral, views focus on morphological variation in the overall outline shape of the sides of the skull and palate (Figure \ref{fig:landmarks}). The result that tenrecs are no more diverse than golden moles in these areas makes intuitive sense: most tenrecs have broad, non-specialised diets \citep{Olson2013} so there is no obvious functional reason why they should have particularly diverse palate morphologies. The different results for our analysis of lateral skull morphologies compared to dorsal and ventral views highlight the importance of using multiple approaches when studying 3D morphological shape using 2D geometric morphometrics techniques \citep{Arnqvist1998}.
%I moved this paragraph up instead of leaving it in a separate caveats section	
	Landmark choice and placement will inevitably influence the results of a geometric morphometrics study. Our interest in broad-scale, cross-taxonomic comparisons of cranial morphology constrained our choice of landmarks to those that could be accurately identified in many different species \citep[e.g.][]{Ruta2013, Goswami2011, Wroe2007}. In contrast, studies that use skulls to characterise morphological variation within species \citep[e.g.][]{Blagojevic2011, Bornholdt2008} or to delineate species boundaries within a clade \citep[e.g.][]{Panchetti2008} tend to focus on more detailed, biologically homologous landmarks \citep{Zelditch2012}. Repeating our analyses with a narrower taxonomic focus may give greater insight into the specific morphological differences among subgroups of tenrecs and golden moles.

	In addition to the differences among the three skull views, our results indicate that, in skulls at least, the overall morphological diversity within tenrecs is not as large as is often assumed \citep[e.g.][]{Eisenberg1969, Olson2013}. Studies of morphological variation are sensitive to the sampling used. If a particular morphotype is over-represented then the similarities among those species will reduce the overall morphological variation within the group \citep{Foote1991}. This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table \ref{tab:diversity}).
	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears.  
	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}. However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}. Variation in skull shape is only one aspect of overall morphology. Quantifying variation in other morphological traits could yield different patterns. Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
	%I combined the paragraph above within the discussion (previously it was part of a separate caveats section)
	While recognising these limitations, our results provide valuable insights into the differences between subjective and quantitative assessments of morphological diversity. 
%**********************************
\section{Conclusions}
	We have presented the first quantitative investigation of morphological diversity in tenrecs. Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the Family. Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required. However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs. 
%*******************************
\section{Acknowledgements} %PeerJ have a separate section for funding acknowledgements
	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments. Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
%********************************
\bibliographystyle{sysbio} 
\bibliography{refs_paper}
